Reinforcement \change{L}earning for \change{O}ptions\\on \change{T}arget \change{V}olatility \change{F}unds\thanks{Supported by ISCRA from Cineca, \email{iscra@cineca.it}.}

### 2023-03-06 tex/m2ef/daluiso_nastasi_pallavicini_polo_rl_for_options_on_tvf.tex
Expand on over-fitting detection

We try to investigate the following hyper-parameters: the FFNN architecture, in particular which feature between the depth and the width of the network is more important, the activation function\change{,} and the learning rate of the optimizer. Moreover, we compare the performances of two well-known optimizers in Machine Learning literature: Nadam \cite{Dozat2016} and RMSprop \cite{Hiton2012}. Since we deal with a free allocation strategy $\alpha$ that can assume negative values, we have chosen among the wide variety of activation functions \change{\cite{Goodfellow2016}} the tanh and the elu. In this way, we can analyze the performance of a saturating activation function and a non-saturating one. Firstly we have performed a grid search on the learning rate starting value and we have found $10^{-3}$ a good choice in terms of speed of learning and avoiding over-fitting. \changeB{Note that since our environment is simulated, over-fitting is easily detected by cross-validation on a set of freshly-generated scenarios which were not seen during optimization.}
 \begin{figure}[h!]
	\centering
	\includegraphics[width=3.4in]{BS_fine_tuning_Nadam_tanh_grey.eps}
	\includegraphics[width=3.4in]{BS_fine_tuning_Nadam_elu_grey.eps}
	\caption{Learning curves of the direct policy algorithm applied to the Black and Scholes \change{scenario}. The solid lines are the loss functions defined in Equation~\eqref{eq:direct_policy_loss} in function of the number of training epochs. Each continuous line represents a different neural network architecture with tanh activation function (top) and elu activation function (bottom). The optimizer adopted is the Nadam with a learning rate of $10^{-3}$. The horizontal grey-dashed line is the conservative option price obtained by maximizing the TVS drift through Equation~\eqref{eq:analytical_solution_free_strategy}}
	\label{fig:result_bs_nadam}
\end{figure}  
 \begin{figure}[h!]
	\centering
	\includegraphics[width=3.4in]{BS_fine_tuning_RMSprop_tanh_grey.eps}
	\includegraphics[width=3.4in]{BS_fine_tuning_RMSprop_elu_grey.eps}
	\caption{Learning curves of the direct policy algorithm applied to the Black and Scholes \change{scenario}. The solid lines are the loss values defined in Equation~\eqref{eq:direct_policy_loss} in function of the number of training epochs. Each continuous line represents a different neural network architecture with tanh activation function (top) and elu activation function (bottom). The optimizer adopted is the RMSprop with a learning rate of $10^{-3}$. The horizontal grey-dashed line is the conservative option price obtained by maximizing the TVS drift through Equation~\eqref{eq:analytical_solution_free_strategy}}
	\label{fig:result_bs_rmsprop}
\end{figure}

>>>>

We try to investigate the following hyper-parameters: the FFNN architecture, in particular which feature between the depth and the width of the network is more important, the activation function\change{,} and the learning rate of the optimizer. Moreover, we compare the performances of two well-known optimizers in Machine Learning literature: Nadam \cite{Dozat2016} and RMSprop \cite{Hiton2012}. Since we deal with a free allocation strategy $\alpha$ that can assume negative values, we have chosen among the wide variety of activation functions \change{\cite{Goodfellow2016}} the tanh and the elu. In this way, we can analyze the performance of a saturating activation function and a non-saturating one. Firstly we have performed a grid search on the learning rate starting value and we have found $10^{-3}$ a good choice in terms of speed of learning and avoiding over-fitting. \changeB{Note that to detect over-fitting one typically compares the performance on one or more training sets with that on corresponding validation sets. Since our environment is simulated, there is no need to explicitly set aside training data for such task, nor to perform $K$-fold validation: indeed we can always generate for the purpose a set of new scenarios which were not seen during optimization.}
 \begin{figure}[h!]
	\centering
	\includegraphics[width=3.4in]{BS_fine_tuning_Nadam_tanh_grey.eps}
	\includegraphics[width=3.4in]{BS_fine_tuning_Nadam_elu_grey.eps}
	\caption{Learning curves of the direct policy algorithm applied to the Black and Scholes \change{scenario}. The solid lines are the loss functions defined in Equation~\eqref{eq:direct_policy_loss} in function of the number of training epochs. Each continuous line represents a different neural network architecture with tanh activation function (top) and elu activation function (bottom). The optimizer adopted is the Nadam with a learning rate of $10^{-3}$. The horizontal grey-dashed line is the conservative option price obtained by maximizing the TVS drift through Equation~\eqref{eq:analytical_solution_free_strategy}}
	\label{fig:result_bs_nadam}
\end{figure}  
 \begin{figure}[h!]
	\centering
	\includegraphics[width=3.4in]{BS_fine_tuning_RMSprop_tanh_grey.eps}
	\includegraphics[width=3.4in]{BS_fine_tuning_RMSprop_elu_grey.eps}
	\caption{Learning curves of the direct policy algorithm applied to the Black and Scholes \change{scenario}. The solid lines are the loss values defined in Equation~\eqref{eq:direct_policy_loss} in function of the number of training epochs. Each continuous line represents a different neural network architecture with tanh activation function (top) and elu activation function (bottom). The optimizer adopted is the RMSprop with a learning rate of $10^{-3}$. The horizontal grey-dashed line is the conservative option price obtained by maximizing the TVS drift through Equation~\eqref{eq:analytical_solution_free_strategy}}
	\label{fig:result_bs_rmsprop}
\end{figure}
